---
title: "Deskriptive Analysis of the Network"
output: html_notebook
---
```{r}
library(igraph)
```


# Descriptive Analysis ---------------------------------------

```{r}
#Number of vertices and edges
vcount(g_l)
ecount(g_l)
gsize(g_l)

count_components(g_l)
is_connected(g_l)
print("Multiedges exist:")
any_multiple(g_l)
```


```{r}
max(degree(g_l))
min(degree(g_l))
# edge_connectivity(g_l)
# vertex_connectivity(g_l)
# cohesion(g_l)
any_multiple(g_l)
diameter(g_l, directed = TRUE, weights = NA)
mean_distance(g_l, directed = TRUE, weights = NA)
transitivity(g_l, type = "average", weights = NA)
#
transitivity(igraph::simplify(g_l, edge.attr.comb = list(weight = "sum")), type = "weighted")
#Only works without multiedges
reciprocity(g_l, ignore.loops = TRUE)
```

```{r}
g_sum <- simplify(g_l, edge.attr.comb = list(weight = "sum"))
#Number of vertices and edges
vcount(g_sum)
ecount(g_sum)
gsize(g_sum)
any_multiple(g_sum)
count_multiple(g_sum)
any_loop(g_sum)
transitivity(g_sum, type = "average") # Only handles directed unweighted, or undirected. 
edge_density(g_sum)
```

```{r}
# Directed eccentricities
ecc_out <- eccentricity(g_l, mode = "out")  
# "out" means distance is measured along outward paths 
# (i.e., from a node to others).

r_out <- radius(g_l, mode = "out")
d_out <- diameter(g_l_s, directed = TRUE, unconnected = TRUE, weights = NA)

cat("Radius (out):", r_out, "\n")
cat("Diameter (directed):", d_out, "\n")
```
```{r}
dist_mat <- distances(g_l_s, mode = "out")  
# This returns an n x n matrix of shortest path distances

# Flatten and remove Inf (unreachable pairs)
finite_dists <- dist_mat[is.finite(dist_mat)] 

hist(finite_dists, 
     breaks = 50,
     main = "Shortest Path Length Distribution",
     xlab = "Path length",
     col = "lightblue")
```

```{r}
triads <- triad_census(g_l)
triads
```
####Checking for small world property

```{r}
transitivity(g_l, type = "average", weights = NA)
mean_distance(g_l_s, directed = TRUE, weights = NA)

```


```{r}
mean_distance(g_l, directed=TRUE, weights = NA)
(log(3674))/(log(log(3674))) # Approxmiation apl, for ? which kind 
```



# Degree Distribution ----------------------------------------


```{r}
in_deg  <- degree(g_l, mode = "in")   # number of incoming edges
out_deg <- degree(g_l, mode = "out")  # number of outgoing edges
all_deg <- degree(g_l, mode = "all")  # in + out
```


```{r}
avg_in  <- mean(in_deg)
med_in  <- median(in_deg)

avg_out <- mean(out_deg)
med_out <- median(out_deg)

avg_all <- mean(all_deg)
med_all <- median(all_deg)

avg_all_s <- mean(all_deg_s)
med_all_s <- median(all_deg_s)

cat("Average in-degree:", avg_in, "Median in-degree:", med_in, "\n")
cat("Average out-degree:", avg_out, "Median out-degree:", med_out, "\n")
cat("Average total degree:", avg_all, "Median total degree:", med_all, "\n")
cat("Average total degree:", avg_all_s, "Median total degree:", med_all_s, "\n")

```
```{r}
in_deg  <- degree(g_l_s, mode = "in")   # number of incoming edges
out_deg <- degree(g_l_s, mode = "out")  # number of outgoing edges
all_deg <- degree(g_l_s, mode = "all")  # in + out
```

```{r}
avg_in  <- mean(in_deg)
med_in  <- median(in_deg)

avg_out <- mean(out_deg)
med_out <- median(out_deg)

avg_all <- mean(all_deg)
med_all <- median(all_deg)

cat("Average in-degree:", avg_in, "Median in-degree:", med_in, "\n")
cat("Average out-degree:", avg_out, "Median out-degree:", med_out, "\n")
cat("Average total degree:", avg_all, "Median total degree:", med_all, "\n")
```

```{r}
# Count nodes based on their degree characteristics
only_out <- sum(in_deg == 0 & out_deg > 0)   # Nodes with only out-degree
only_in <- sum(out_deg == 0 & in_deg > 0)    # Nodes with only in-degree
both <- sum(in_deg > 0 & out_deg > 0)        # Nodes with both in-degree and out-degree

# Print results
cat("Nodes with only out-degree:", only_out, "\n")
cat("Nodes with only in-degree:", only_in, "\n")
cat("Nodes with both in-degree and out-degree:", both, "\n")
```


```{r}
# Degree distribution
dd_g <- degree_distribution(g_l_s, cumulative = FALSE)
cumdd_g <- degree_distribution(g_l_s, cumulative = TRUE)
```

```{r}
plot(dd_g, type="o", col="blue", xaxt="n", xlab="Degree", ylab="Relative Frequency")
axis(1, at=NULL, labels=TRUE)
```
```{r}
plot(cumdd_g, type="o", col="blue", xaxt="n", xlab="Degree", ylab="Cummulative Frequency")
axis(1, at=NULL, labels=TRUE)
```

```{r}
# 2. Plot separate histograms (base R)
par(mfrow=c(1,2))  # 2 plots side-by-side for convenience

plot(dd_g, type="s", col="blue", xaxt="n", xlab="Degree", ylab="Relative Frequency",
     main = "Degree Distribution")
axis(1, at=NULL, labels=TRUE)
plot(cumdd_g, type="s", col="blue", xaxt="n", xlab="Degree", ylab="Cumulative Frequency",
     main = "Cumulative Degree Distribution")
axis(1, at=NULL, labels=TRUE)

```



```{r}
# 2. Plot separate histograms (base R)
par(mfrow=c(1,2))  # 2 plots side-by-side for convenience

hist(in_deg,
     breaks = seq(min(in_deg), max(in_deg), by = 1),
     main = "In-degree Distribution",
     xlab = "In-degree",
     col = "lightblue",
     border = "white")

hist(out_deg,
     breaks = seq(min(out_deg), max(out_deg), by = 1),
     main = "Out-degree Distribution",
     xlab = "Out-degree",
     col = "black",
     border = "white")

```
```{r}
plot(
  in_deg, out_deg,
  xlab = "In-degree",
  ylab = "Out-degree",
  main = "In-degree vs. Out-degree"
)

```


```{r}
par(mfrow = c(1, 3))  # 3 plots side by side

hist(in_deg,
     main = "In-degree Distribution",
     xlab = "In-degree",
     col = "lightblue",
     breaks = 50)

hist(out_deg,
     main = "Out-degree Distribution",
     xlab = "Out-degree",
     col = "lightgreen",
     breaks = 50)

hist(all_deg,
     main = "Total Degree Distribution",
     xlab = "Total degree (in+out)",
     col = "lightgray",
     breaks = 50)

```
```{r}
deg_counts <- table(out_deg)
plot(
  as.numeric(names(deg_counts)),  # x-axis: degree values
  as.numeric(deg_counts),         # y-axis: counts of those degrees
  log = "xy",                     # log-log scale
  xlab = "In-degree (log scale)",
  ylab = "Frequency (log scale)",
  main = "Out-degree Distribution (log-log)"
)

```


```{r}
# Quick check in log space:
plot(table(in_deg), log="xy", 
     main = "In-degree distribution (log-log)",
     xlab = "In-degree", ylab = "Frequency")

```


```{r}
dSortedg <-sort.int(degree(g_l_s, mode = "in"),decreasing=TRUE,index.return=FALSE)
head(dSortedg, n = 10)

dSortedg <-sort.int(degree(g_l_s, mode = "out"),decreasing=TRUE,index.return=FALSE)
head(dSortedg, n = 10)
```



```{r}
#out_strength TOTAL exposure
out_strength <- strength(g_l_s, mode = "out", weights = E(g_l_s)$weight)

print(data.frame(head(round(sort(out_strength, decreasing = T)/1000000000, 3), n = 10)))


```





# Centrality Measures ---------------------------------------


```{r}
degcent <-   centr_degree(g_l, mode="out", loops = TRUE)
#degcent
closecent <- centr_clo(g_l, mode = "out")
#closecent
betwcent <-  centr_betw(g_l, directed=TRUE)
#betwcent
```


```{r}
eig_centrality <- eigen_centrality(g_l, directed = TRUE, weights = NA)
eig_centrality$value
```
```{r}
# This is alpha measure for Katz, 0.9 to make sure it is smaller than the dominant eigenvalue
alpha <- 0.9/11
```


```{r}
#evcent <-    centr_eigen(g_l, directed=TRUE)
#evcent should only be used in strongly connected graphs or undirected
katzcent <-  igraph::alpha_centrality(g_l, alpha=alpha, loops = TRUE, weights = NA)
#katzcent#katzcentNULL
# alpha: 0.2 fast decay = short paths important, 0.9 longer paths important
prcent <-  page_rank(g_l, directed=TRUE)
#prcent
```


```{r}
g_no_multiedges <- simplify(g_l, remove.multiple = TRUE, remove.loops = FALSE)
alpha_centrality(g_no_multiedges, alpha = 0.2, loops = FALSE, tol = 1e-7, weights = NA)
```



```{r}
degcent$centralization
closecent$centralization
betwcent$centralization
katzcent$centralization
prcent$centralization
```

```{r}
# Weighted degree centrality (in-strength and out-strength)
in_strength <- strength(g_l, mode = "in", weights = E(g_l)$weight)
out_strength <- strength(g_l, mode = "out", weights = E(g_l)$weight)

# Combine results into a data frame
weighted_degree <- data.frame(
  Bank = V(g_l)$name,
  In_Strength = in_strength,
  Out_Strength = out_strength
)

print(weighted_degree)
```
```{r}
# Betweenness centrality (weighted)
w_betwcent <- betweenness(g_l, directed = TRUE, weights = E(g_l)$weight)

# Add to the data frame
weighted_degree$Betweenness = w_betwcent
print(weighted_degree)
```
```{r}
summary(E(g_l)$weight)
any(E(g_l)$weight <= 0) 
min(E(g_l)$weight)
```
```{r}
# Calculate Katz centrality (directed, with weights)
katz_centrality <- eigen_centrality(g_l, directed = TRUE, weights = E(g_l)$weight, options = list(alpha = alpha))$vector

# Add to the data frame
weighted_degree$Katz = katz_centrality
print(weighted_degree)
```
```{r}
# PageRank (weighted)
pagerank_scores <- page_rank(g_l, directed = TRUE, weights = E(g_l)$weight)$vector
# Add to the data frame
weighted_degree$PageRank = pagerank_scores
print(weighted_degree)
```



# Component and Cluster Analysis
```{r}
# This might be deleted as it does not make much sense as there is basically only one cluster of weakly connected component
# Find weakly connected components
wcc <- components(g_l, mode = "strong")

# Number of components
num_components <- wcc$no
component_sizes <- table(wcc$csize)
```


### Assortativity 

```{r}
# Degree assortativity
degree_assort <- assortativity_degree(g_l, directed = TRUE)


# Weighted assortativity
weighted_assort <- assortativity(g_l, types1 = strength(g_l, mode = "out", weights = E(g_l)$weight), 
                                    types2 = strength(g_l, mode = "in", weights = E(g_l)$weight))

cat("Degree assortativity coefficient:", degree_assort, "\n")
cat("Weighted assortativity coefficient:", weighted_assort, "\n")
```


Question:
What exactly does normalize do again, should it be used
since evcent should not be used weakly connected what are other good measures
Is pagerank even good measure for financial network
Analyze with weighs or without