---
title: "Processing Network"
output: html_notebook
---

This notebooks
Input: Dataframe
Output: 
- g: igraph from dataframe
- g_l: largest connected component of g
- g_l_s: largest connected simplified component igraph from g -> g_l -> g_l_s (summed edges = simplified)
- g_topx: most important X amount of banks simplified  g_l_s -> g_topx 
- g_sib : only systemically important banks, simplified g_l_s -> g_sib

- net_l_s: network object of g_l_s
- net_topx: network object of g_topx
- net_sib: network object of g_sib

```{r include=FALSE}
#Install and Load required packages
library('here')
library('dplyr')
library('readxl')
library('stringr')
library('purrr')
library('tidyr')
library('stringdist')
library('intergraph')
library('ggraph')
library('visNetwork')
library('igraph')

```

Read and process data
```{r}
#Reading in processed data
df <- read.csv("./Processing/processed_loan_v3.csv")
```

```{r}
# Group and sum the loans together, rename the columns
df_agg <- df %>%
  group_by(LoanID, Lender, Borrower) %>%
  summarise(
  AssignedLoanShare = sum(AssignedLoanShare),
  Roles = paste(unique(Role), collapse = ", "),
  Sector = first(Sector),
  MaturityDate = first(Maturity.Date),
  IssueDate = first(Issue.Date),
  LenderRegion = first(LenderRegion),
  LenderMarket = first(LenderMarket), 
  BorrowerDomicile = first(BorrowerDomicile),
  TrancheType = first(TrancheType),
  TrancheCurrency = first(TrancheCurrency),
  Seniority = first(Seniority)
  # etc...
  )

```

Make g from dataframe
```{r}
#g being the large dataframe from the processed data turned into an igraph object, not processed
g <- graph_from_data_frame(
  d = df_agg[, c("Lender", "Borrower", "AssignedLoanShare", "Roles")],
  directed = TRUE
)

# Set the 'AssignedLoanShare' as the edge weight
E(g)$weight <- E(g)$AssignedLoanShare

# Optionally keep 'Roles' as an edge attribute:
#E(g)$roles <- df_agg$Roles
```


Create subgraph g_l being the largest connected component of g 
```{r}
# Identify connected components
components <- igraph::components(as_undirected(g))

# Find the size of the largest connected component
print(max(components$csize))

#Could use largest_component() but does not retain VertexID of original graph - could be used later is not needed

# Find the component ID of the largest connected component
largest_component_id <- which.max(components$csize)

# Create a subgraph of the largest connected component
g_l <- induced_subgraph(g, vids = which(components$membership == largest_component_id))
```

```{r}
# This is a fix for symbolically weighted edges, for correctly calculating centrality measures later
# They are just the remains of Sole lender 100% scale factor calculation
E(g_l)$weight[E(g_l)$weight == 0] <- 0.1
```


Simplify largest connected component g_l into g_l_s, summing the edges between two nodes
Removing attributes not used for current analysis goals
```{r}
# g_l_s being the simplified graph, summing all weights between the same two nodes. 
g_l_s <- igraph::simplify(
  g_l, 
  edge.attr.comb = list(weight = "sum"),
  remove.loops = TRUE
)
g_l_s <- delete_edge_attr(g_l_s, "Roles")
g_l_s <- delete_edge_attr(g_l_s, "AssignedLoanShare")
E(g_l_s)$weight[E(g_l_s)$weight == 0.1] <- 1
E(g_l_s)$weight <- round(E(g_l_s)$weight)

# Confirm Mulitedges have been summed:
print("Multiedges exist:")
any_multiple(g_l_s)
```

# Subgraph Top 10s
Compute (Sample) Top 10 largest borrowers and sellers by USD Amount and create Subgraph
```{r}
# Compute total out and in weights
out_strength <- strength(g_l_s, mode = "out", weights = E(g_l_s)$weight)
in_strength <- strength(g_l_s, mode = "in", weights = E(g_l_s)$weight)

# Select top lenders and borrowers
top_lenders <- names(sort(out_strength, decreasing = TRUE))[1:10]
top_borrowers <- names(sort(in_strength, decreasing = TRUE))[1:10]

# Combine unique nodes
important_nodes <- unique(c(top_lenders, top_borrowers))

# Find their neighbors
neighbors <- unique(unlist(igraph::neighborhood(g_l_s, order = 1, nodes = important_nodes, mode = "all")))

# Create the subgraph
#sub_g <- induced_subgraph(g_l, vids = neighbors) # This makes important nodes + their neighbors in the network
g_topx <- induced_subgraph(g_l_s, vids = important_nodes) # This makes it only the important nodes are in the network
```


Verify correct subgraph has been implemented
```{r}
#Number of vertices and edges
vcount(g_topx)
ecount(g_topx)
gsize(g_topx)
count_components(g_topx)
is_connected(g_topx)
print("Multiedges exist:")
any_multiple(g_topx)
```


Building subgraph of 29 globally systemically important banks
```{r}
importantbanks <- c(
  'JP MORGAN CHASE',
  'CITI',
  'HSBC',
  'AB CHINA',
  'BANK OF AMERICA',
  'BANK OF CHINA',
  'BARCLAYS',
  'BNP PARIBAS',
  'CHINA CONSTRUCTION BANK',
  'DEUTSCHE BANK',
  'GOLDMAN SACHS',
  'CREDIT AGRICOLE',
  'ICB CHINA',
  'MUFG',
  'UBS',
  'BANK OF COMMUNICATIONS',
  'BNY',
  'BPCE',
  'ING BANK',
  'MIZUHO',
  'MORGAN STANLEY',
  'ROYAL BANK OF CANADA',
  'BANCO SANTANDER',
  'SOCIETE GENERALE',
  'STANDARD CHARTERED',
  'STATE STREET BANK',
  'SMBC',
  'TORONTO DOMINION BANK',
  'WELLS FARGO'
)
g_sib <- induced_subgraph(g_l_s, vids = importantbanks) 
```


Make the g_sib a connected network
```{r}
## 1.  locate the G-SIB vertices in the big graph
gsib_vids <- which(V(g_l_s)$name %in% importantbanks)

## 2.  collect their 1-hop neighbourhoods
##     - order = 1 …… reach exactly one step
##     - mode  = "all" …… follow both in- and out-going edges
ego_list  <- neighborhood(g_l_s,
                          order = 1,
                          nodes = gsib_vids,
                          mode  = "all")

## 3.  union the vertex sets and build the induced subgraph
ego_nodes <- unique(unlist(ego_list))
g_ego    <- induced_subgraph(g_l_s, vids = ego_nodes)

## 4.  quick sanity checks
cat("nodes:", vcount(g_ego), "  edges:", ecount(g_ego), "\n")
cat("components:", components(g_ego)$no, "\n")   # should now be 1
```
```{r}

wire_paths_k <- function(g, gsib_names,
                         k    = 2,       # maximum hop length
                         mode = "all") { # "all", "out", or "in"

  gsib_vids <- which(V(g)$name %in% gsib_names)
  pairs     <- combn(gsib_vids, 2, simplify = FALSE)

  keep_nodes <- gsib_vids                    # start with the G-SIBs

  for (p in pairs) {
    d <- distances(g, v = p[1], to = p[2],
                   mode = mode, weights = NA)     # ← IGNORE WEIGHTS
    if (is.finite(d) && d <= k) {
      sp <- shortest_paths(g,
                           from    = p[1],
                           to      = p[2],
                           mode    = mode,
                           weights = NA)$vpath[[1]] # ← IGNORE WEIGHTS
      keep_nodes <- c(keep_nodes, sp)
    }
  }

  induced_subgraph(g, vids = unique(keep_nodes))
}

## --------- run it ----------------------------------------------------------
g_wire <- wire_paths_k(g_l_s, importantbanks, k = 2)  # or k = 3 if needed
cat("nodes:", vcount(g_wire),
    "  edges:", ecount(g_wire),
    "  components:", components(g_wire)$no, "\n")


```



Preparing network objects for further use (ERGM)
```{r}
net_l_s <- intergraph::asNetwork(g_l_s)
net_topx <- intergraph::asNetwork(g_topx)
net_sib <- intergraph::asNetwork(g_sib)
net_wire <- intergraph::asNetwork(g_wire)

network::set.edge.attribute(net_l_s, "weight", igraph::get.edge.attribute(g_l_s, "weight"))

# Verify edge weights (replace "weight" with actual edge attribute name)
#network::set.edge.attribute(net, "weight", igraph::get.edge.attribute(g_l, "weight"))

```

```{r}
#Check model formation worked as intended
summary(net_l_s)
network::list.edge.attributes(net_l_s)
```





